TaskMiner: Automatic Identification of Tasks.

### 2018-08-06 docs/SBLP/paper.tex
SBLP published with DOI

%% Conference information (used by SIGPLAN proceedings format)
%% Supplied to authors by publisher for camera-ready submission
\acmConference[SBLP'18]{XXII Brazilian Symposium on Programming Languages}{2018}{Brasil}
\acmYear{2018}
\acmISBN{978-1-4503-6480-5/18/09}
\acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}
\fi

@@

\title[TaskMiner: Identifica\c{c}\~{a}o Autom\'{a}tica de Tarefas]
{TaskMiner: Identificação Automática de Tarefas}

\author{Pedro Ramos, Gleison Souza, Guilherme Leobas, Fernando Magno Quint\~{a}o Pereira}
%\authornote{with author1 note}          %% \authornote is optional;
%\orcid{nnnn-nnnn-nnnn-nnnn}
\affiliation{
  %\position{Researcher}
  %\department{DCC}
  \institution{UFMG}
%  \streetaddress{6627 Antonio Carlos Avenue}
%  \city{Belo Horizonte}
%  \state{Minas Gerais}
 % \postcode{31.270-213}
 % \country{Brazil}
}
\email{[pedroramos, gleison.mendonca, guilhermel, fernando]@dcc.ufmg.br}

@@

\begin{abstract}
Este artigo apresenta \Taskminer{}, uma ferramenta que encontra paralelismo de tarefas
em código C automaticamente. \Taskminer{} lida com problemas clássicos de paralelismo irregular 
como a delimitação simbólica de regiões de memória, remoção de dependências
estáticas espúrias, detecção de condições de corrida, e, principalmente, a avaliação do custo do paralelismo. Para solucioná-los,
\Taskminer{} implementa uma série de otimizações em representa\-ção intermedi-ária do LLVM, que analisam código C e inserem anotações OpenMP automaticamente. \Taskminer{} prova-se eficaz ao encontrar paralelismo apontado manualmente em benchmarks como \textsf{BSC-Bots}~\cite{Duran09}, produzindo programas tão rápidos ou mais velozes que as versões sequenciais e anotadas manualmente. \Taskminer{} também é capaz de encontrar paralelismo escondido em programas sequenciais, sem intervenção humana.
\end{abstract}

@@

\keywords{paralelismo, tarefas, OpenMP, compiladores}

>>>>

%% Conference information (used by SIGPLAN proceedings format)
%% Supplied to authors by publisher for camera-ready submission
\copyrightyear{2018} 
\acmYear{2018} 
\setcopyright{othergov}
\acmConference[SBLP 2018]{XXII Brazilian Symposium on Programming Languages}{September 20--21, 2018}{SAO CARLOS, Brazil}
\acmPrice{15.00}
\acmDOI{10.1145/3264637.3264639}
\acmISBN{978-1-4503-6480-5/18/09}

\startPage{1}
\fi

@@

\title[TaskMiner: Automatic Identification of Tasks.]
{TaskMiner: Automatic Identification of Tasks.}

\author{Pedro Ramos, Gleison Souza, Guilherme Leobas, Fernando Magno Q. Pereira}
%\authornote{with author1 note}          %% \authornote is optional;
%\orcid{nnnn-nnnn-nnnn-nnnn}
\affiliation{
  %\position{Researcher}
  %\department{DCC}
  \institution{UFMG}
%  \streetaddress{6627 Antonio Carlos Avenue}
%  \city{Belo Horizonte}
%  \state{Minas Gerais}
 % \postcode{31.270-213}
 % \country{Brazil}
}
\email{[pedroramos, gleison.mendonca, guilhermel, fernando]@dcc.ufmg.br}

@@

\begin{abstract}
This paper presents \Taskminer{}, a tool that automatically finds task parallelism in C code. \Taskminer{} solves classic problems of irregular parallelism, such as finding the memory ranges accessed by tasks, removing spurious static dependencies, detecting data-racing conditions and, most importantly, assessing the cost of parallelism for a given task or program. \Taskminer{} implements a suite of optimizations in LLVM's intermediate representation, which in the end insert \textsf{OpenMP} annotations to the code automatically, exposing task parallelism. \Taskminer{} finds parallelism that was previously manually appointed in benchmarks such as \textsf{BSC-Bots}, producing programs that are as fast or even faster than their sequential and manually annotated counterparts. \Taskminer{} also finds hidden parallelism in sequential programs, without human intervention.
\end{abstract}

@@

\keywords{parallelism, tasks, OpenMP}
